### 2015-04-08 related.tex
Added comparision to Burckhardt's ECOOP15

Our contract language is inspired by the axiomatic description of RDT semantics
proposed by~\cite{Burckhardt2014}. While they use axioms for formal
verification of correctness of an RDT implementation, we utilize them as a
means for the user to express the desired consistency guarantees in the
application. Similar to their work, our contract language does not incorporate
real (i.e., wall-clock) time. Hence, it cannot describe store semantics such as
recency or bounded-staleness guarantees offered by certain
stores~\cite{Pileus}.

>>>>

Our contract language and system model is inspired by the axiomatic description
of RDT semantics proposed by~\cite{Burckhardt2014}. While they use axioms for
formal verification of correctness of an RDT implementation, we utilize them as
a means for the user to express the desired consistency guarantees in the
application. Operational semantics of \name (described in the accompanying tech
report~\cite{techrep}) describe an operational manifestation of our system
model.  ~\cite{Burckhardt2015} also presents an operational model of a
replicated data store that is based on the abstract system model presented in
~\cite{Burckhardt2014}. Their claims about the expressivity and practicality of
the system model vindicate ours.  However, both differ in the way they aim to
empower the application programmer. In~\cite{Burckhardt2015}, they expose their
operational model to the application programmer, along with primitives, such as
\cf{push}, \cf{pull} and \cf{fetch}, that make it easy to \emph{implement} the
required consistency and isolation guarantees. In contrast, \name completely
abstracts its operational model, and instead relies on contract classification
to \emph{choose} appropriate consistency and isolation levels.  Similar
to~\cite{Burckhardt2014} and~\cite{Burckhardt2015}, our system model does not
incorporate real (i.e., wall-clock) time. Hence, our contract language cannot
describe store semantics such as recency or bounded-staleness guarantees offered
by certain stores~\cite{Pileus}.
